---
title: "Shrub-Lizard Data Method 2 Test Repo"
author: "Mario"
date: '2021-03-31'  
output: html_document
---
###The following is a test repo to connect the density of shrub individuals within the Carrizo Plain National Monument to the data collected from the Lizard Telemetry Project.
### I have tried several different ways. It seems the first way was the closes but it only works for one specific Lat/Long

```{r}
##Load Packages
library(data.table)
library(sp)
library(rgdal)
library(ggplot2)
library(dplyr)
```
###Maps
```{r}
##I tried creating a mao here to get a better visualizaion of the points. I read in the Shrub datafile I got from pinning Shrubs on Google Earth.
shrub_dat = fread("Untitled_layer.csv")
shrub_dat = as.data.table(shrub_dat)
```

```{r}
coordinates(shrub_dat) = c("x", "y")
crs.geo1 = CRS("+proj=longlat")
proj4string(shrub_dat) = crs.geo1

plot(shrub_dat, pch = 20, col = "steelblue")
```
```{r}
carrizo = readOGR(dsn = path.expand("mygeodata"),layer = "Untitled_Project_1-polygon")
```
```{r}
plot(carrizo)
points(shrub_dat, pch = 20, col = "orange")
```
```{r}
###This is a quick map layering the Shrub coordinates that I got from Google Earth and the Lizard coordinates i got from Chris' tidied repo. I only located 50 shrubs to test the rest of the code before i start Tagging all the shrubs in an area.
library(ggmap)
library(geosphere)
shrubs <- read.csv("Shrubs.csv")
lizard <- read.csv("Lizards.csv")
lizards <- read.csv("tidy_telemetry_Carrizo.csv")

register_google(key="AIzaSyBurG6FR6I4uc_nRUr6TY118dCsnM0tsiE")
carrizo <- get_map(location = c(lon = -119.62, lat = 35.11941), zoom = 14, maptype = "satellite")
carrizo
site.wide.map <- ggmap(carrizo)
site.wide.map <- site.wide.map +
  geom_point(data=shrubs, aes(x=X, y=Y, color = Site), alpha = 1, size =0.1, shape = 0, color = "green", show.legend = FALSE) +
  labs(x = "longitude", y = "latitude") + theme(axis.title.x = element_blank()) + theme(axis.title.y = element_blank())
site.wide.map <- site.wide.map +
  geom_point(data=lizards, aes(x=long, y=lat, color = Site), alpha = 1, size =0.1, shape = 0, color = "red", show.legend = FALSE) +
  labs(x = "longitude", y = "latitude") + theme(axis.title.x = element_blank()) + theme(axis.title.y = element_blank())
site.wide.map
##Generating the map with the datasets is easy. Finding the number of individuals per area is thr tricky part now.
```
###Trying to set up the Code:
```{r}
#So I tried using this to try and run the code. What this does is that it will give True or False depending on how many individuals are within a ppint. I tried setting it up to reference a dataset (the lizard one) but it seems that it will only work with one specific coordinate. I tried doing df$lat and df$long for the lizard data but i keep getting errors

#Ok so this works for ONE SPECIFIC POINT! Now how do i make it work for an entire dataset...
coord <- cbind("longitude" = shrubs$X, "latitude" = shrubs$Y) #Set up the Lat/Lng for shrub data
coordliz <- cbind("longitude" =  lizards$long, "latitude" = lizards$lat) #Set up the Lat/Lng for Lizard data

###This bit below is where it would output if the points are within 5m from a specific point or not.
coord_df <- data.frame(coord, 
                       within_5m = geosphere::distHaversine(
                           coord, 
                           c(-119.6290589,  35.12090732) ###This is where the error occurs. It only allows for one specific point and not for multiple.
                       ) < 5 )  

str(coord_df$within_5m)
table(coord_df$within_5m) ###This is the utput showing how many are within the designated distance (True) and how many are not (False). If I can get this to work for an entire dataset we are set!
```

```{r}
###So now i tried to use buffers since i've seen a bunch of examples online of people using the sf, raster and sp functions to run this but again it seems like it does not want to work.
###Trying with buffers
library(rgeos)
library(raster)
library(sf)
library(sp)
geoliz = st_as_sf(lizards,coords=c("long","lat"))
geoshrubs = st_as_sf(shrubs,coords=c("X", "Y"))
st_crs(geoliz) = st_crs(geoshrubs)

geoliz_km <- geoliz %>% st_set_crs(4326) %>% st_transform("+proj=utm +zone=11 +datum=WGS84 +units=km")
geoshrubs_km <- geoshrubs %>% st_set_crs(4326) %>% st_transform("+proj=utm +zone=11 +datum=WGS84 +units=km")
```
```{r}
###Set up the lizard data as a buffer.
liz_buffer = st_buffer(geoliz_km, 1)
liz_shrubs = st_intersection(liz_buffer, geoshrubs_km)
```
```{r}
dim(liz_shrubs)
liz_shrubs$area = st_area(liz_shrubs) ###The problem is is that with the areas keep outputting as 0^KM.
```
```{r}
###Here i tried setting up polygons with the lizard data using sp and rgdal.
###Trying with Polygons
library(sp)
library(rgdal)
radius <- 0.0002
###Below i tried to set up polygons within 5m of a lizard point. I thought something like this would work but againit doesn't seem to output what we want.
yPlus <- lizards$lat+radius
yMinus <- lizards$lat-radius
xPlus <- lizards$long+radius
xMinus <- lizards$long-radius

#Set up the area for the points
square=cbind(xMinus,yPlus,
             xPlus,yMinus,
             xMinus,yMinus,
             xMinus,yPlus)

ID = lizards$relocation_ID

polys <- SpatialPolygons(mapply(function(poly, id) 
        {
      xy <- matrix(poly, ncol=2, byrow=TRUE)
      Polygons(list(Polygon(xy)), ID=id)
      }, 
    split(square, row(square)), ID),
    proj4string=CRS(as.character("+proj=utm +zone=11 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0")))
##Everything here seems to just be a set up to plot the points and does not seem to entirely work.
plot(polys)
```

###So Far
So far it seems that the first method might be the most promising but I have been struggling to get the code to read a dataframe instead of just one specific points. I thought buffers could possibly work but it might not for this case. 